---
title: "appliances usage"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(ggplot2)
library(meta)
library(metafor)
library(metadat)
library(haven)
library(writexl)
library(openxlsx)
library(dplyr)
library(stringr)
library(wesanderson)
library(ggrepel)
options(scipen = 999)
```

```{r}
# load datasets  for usage 
data_usage <- data.frame()
# filter to a needed dependent variable
data_usage <- appliances %>% 
                  filter(dep_variable_purchase_category == "energy use after switching to a more efficient appliance")
# exclude the outliers
# data_usage <- data_usage %>% 
                  # filter(coefficient > -2,
                      # coefficient < 2)
# data_usage <- data_usage %>% 
                  # filter(percent_change > -2,
                    # percent_change < 2)
unique_studies_usage <- unique(data_usage$study_ID)
```

```{r}
data_usage$percent_change <- ifelse(is.na(data_usage$percent_change),
                                    data_usage$coefficient,
                                    data_usage$percent_change)

data_usage$percent_change <- data_usage$percent_change*100

data_usage$percent_change_ci <- ifelse(data_usage$study_ID == "130",
                                       data_usage$coefficient_se*100/8260.69,
                                       ifelse(data_usage$study_ID == "140",
                                              data_usage$coefficient_se*100/437.369,
                                              data_usage$coefficient_se*100)
                                       )
data_usage <- data_usage %>% 
                  filter(percent_change > -25,
                    percent_change < 25)

```

```{r}
# observe summary statistics
summary(data_usage)

# Count the occurrences
count <- table(data_usage$appliance)
print(count)

# Group by appliance and calculate summary statistics
summary_stats <- data_usage %>%
  group_by(appliance) %>%
  summarise(
    mean_percent_change = mean(percent_change),
    min_percent_change = min(percent_change),
    max_percent_change = max(percent_change),
    mean_coefficient = mean(coefficient),
    min_coefficient = min(coefficient),
    max_coefficient = max(coefficient),
    #mean_tstat = mean(t_stat),
    mean_tstat_abs = mean(abs(t_stat))
  )

# Print the summary statistics
print(summary_stats)

# why is lighting showing a positive change - does that make sense based on primary studies' results?
```

```{r}

### FOREST PLOTS ### 
fp <- ggplot(data=data_usage, aes(x=authors, y=percent_change, ymin=percent_change - percent_change_ci, ymax=percent_change + percent_change_ci, colour = appliance)) +
        geom_pointrange(size=0.5) + 
        geom_hline(yintercept=1, lty=2) +  # add a dotted line at x=1 after flip
        coord_flip() +  # flip coordinates (puts labels on y axis)
        xlab("Authors") + ylab("Mean Percentage Change") +
        theme_bw()  + geom_label_repel(aes(label = paste0(round(percent_change, 2), "%")), size = 2, colour = "black", max.overlaps = 15)
print(fp)

# we can average by author
# or average by appliance

### FREQUENCY TABLES AND DISTRIBUTIONS
ggplot(data_usage, aes(x = percent_change, y = percent_change_ci , colour = appliance)) +
  # scale_y_continuous(limits = c(-0.05,.5))+
  geom_point(size = 2, alpha = 0.25) +
  #geom_jitter(width = .1, alpha = .25) +
  labs(x = "percent_change", y = "variance") +
  facet_wrap(vars(data_usage$intervention))+ 
  theme_bw()
```
```


```{r}
### MULTI-LEVEL MODEL ###

# Step 1: Create a meta-analysis model
meta_model1_usage <- rma(z_value, z_variance, data = data_usage, method = "FE", mods = ~ intervention+0)
meta_model2_usage <- rma(z_value, z_variance, data = data_usage, method = "FE", mods = ~ appliance+0)
meta_model3_usage <- rma(z_value, z_variance, data = data_usage, method = "REML", mods = ~ intervention+0)
meta_model4_usage <- rma(z_value, z_variance, data = data_usage, method = "REML", mods = ~ appliance+0)

# Step 2: Fit the meta-analysis model
meta_result1_usage <-rma.mv(z_value, z_variance, mods =  ~ intervention+0, 
                               random = ~ as.factor(sr_no) | as.factor(study_ID), data = data_usage, method = "FE")
meta_result2_usage <-rma.mv(z_value, z_variance, mods =  ~ appliance+0, 
                               random = ~ as.factor(sr_no) | as.factor(study_ID), data = data_usage, method = "FE")
meta_result3_usage <-rma.mv(z_value, z_variance, mods =  ~ intervention+0, 
                               random = ~ as.factor(sr_no) | as.factor(study_ID), data = data_usage, method = "REML")
meta_result4_usage <-rma.mv(z_value, z_variance, mods = ~ appliance+0, 
                               random = ~ as.factor(sr_no) | as.factor(study_ID), data = data_usage, method = "REML")
# make graphs from this
summary(meta_model1_usage)
# fixed effects by intervention
# choice architecture, feedback, label, rebate significant negative
summary(meta_result1_usage)
# fixed effects multi-level by intervention
# choice architecture, feedback, label, rebate significant negative
summary(meta_model2_usage)
# fixed effects by appliance
# heat pump, light, fridge significant negative - rebound in AC and TV
summary(meta_result2_usage)
# fixed effects multi-level by appliance
# heat pump, light, fridge significant negative - rebound in AC and TV
summary(meta_model3_usage)
# random effects by intervention
# choice architecture and label significant negative
summary(meta_result3_usage)
# random effects multi-level by intervention
# choice architecture and label significant negative
summary(meta_model4_usage)
# random effects by appliance
# AC and light significant negative - rebound only in tv
summary(meta_result4_usage)
# random effects multi-level by appliance
# AC and light significant negative - rebound only in tv
```


```{r}
# subset dataset for each appliance and intervention in usage

<<<<<<< HEAD
appliancesusage$appliance <- with(appliancesusage, case_when(
  tv == 1 ~ "TV",
  ac == 1 ~ "Air-Conditioner",
  refrigerator == 1 ~ "Refrigerator",
  diswasher == 1 ~ "Dishwasher",
  washing_machine == 1 ~ "Washing Machine",
  clothes_dryer == 1 ~ "Clothes Dryer",
  heat_pump == 1 ~ "Heat Pump",
  lighting == 1 ~ "Lighting",
  water_heater == 1 ~ "Water Heater",
  TRUE ~ NA_character_
))
```

```{r}
##dishwasher
### RANDOM EFFECTS ###
m.gen_usage_dishwasher <- metagen(data = data_usage_dishwasher,
                                  TE = z_value,
                                  seTE = z_variance,
                                  studlab = authors,
                                  sm = "ZCOR",
                                  fixed = FALSE,
                                  random = TRUE,
                                  backtransf = F)
=======
#data_usage_washing <- data_usage %>% 
                  #filter(washing_machine == 1)
>>>>>>> 0a5f01a75e7111d41d1ea36bd1f02e67b1714114

data_usage_dishwasher <- data_usage %>% 
                  filter(diswasher == 1)

#data_usage_dryer <- data_usage %>% 
                  #filter(clothes_dryer == 1)

data_usage_refrigerator <- data_usage %>% 
                  filter(refrigerator == 1)

data_usage_heat_pump <- data_usage %>% 
                  filter(heat_pump == 1)

data_usage_lighting <- data_usage %>% 
                  filter(lighting == 1)

#data_usage_water <- data_usage %>% 
                  #filter(water_heater == 1)

data_usage_ac <- data_usage %>% 
                  filter(ac == 1)

#data_usage_tv <- data_usage %>% 
                  #filter(tv == 1)
```

```{r}
## creating matrix of appliance and intervention
## check whether all combinations are in here

##dishwasher / interventions

data_usage_dishwasher_information <- data_usage_dishwasher %>% 
                                 filter(information == 1)

data_usage_dishwasher_rebate <- data_usage_dishwasher %>% 
                                 filter(rebate == 1)

##refrigerator

data_usage_refrigerator_information <- data_usage_refrigerator %>% 
                                 filter(information == 1)

data_usage_refrigerator_rebate <- data_usage_refrigerator %>% 
                                 filter(rebate == 1)

data_usage_refrigerator_label <- data_usage_refrigerator %>% 
                                 filter(label == 1)

##heatpump
data_usage_heat_pump_information <- data_usage_heat_pump %>% 
                                 filter(information == 1)

data_usage_heat_pump_feedback <- data_usage_heat_pump %>% 
                                 filter(feedback == 1)

data_usage_heat_pump_rebate <- data_usage_heat_pump %>% 
                                 filter(rebate == 1)

##lighting
data_usage_lighting_information <- data_usage_lighting %>% 
                                 filter(information == 1)

data_usage_lighting_feedback <- data_usage_lighting %>% 
                                 filter(feedback == 1)
##air con
data_usage_air_information <- data_usage_air %>% 
                                 filter(information == 1)
data_usage_air_feedback <- data_usage_air %>% 
                                 filter(feedback == 1)
data_usage_air_rebate <- data_usage_air %>% 
                                 filter(rebate == 1)
```

```{r}
### RANDOM EFFECTS MODEL ###
##washing machine
m.gen_usage_washing <- metagen(TE = z_value,
                 seTE = z_variance,
                 data = data_usage_washing,
                 studlab = Authors,
                 sm = "ZCOR",
                 fixed = FALSE,
                 random = TRUE,
                 backtransf = F,
                 )

## forest plot of usage

png(file = "forestplot_washing.png", width = 5000, height = 2000, res = 500)
forest.meta(m.gen_usage_washing,
           leftcols = c("Authors", "Intervention"),
           digits =6,
           col.random = "Red",
           xlab = "Effect Sizes",
           col.square = "Blue")

### FIXED EFFECTS MODEL ###
  
m.gen_usage_washing <- metagen(TE = z_value,
                 seTE = z_variance,
                 data = data_usage_washing,
                 studlab = Authors,
                 sm = "ZCOR",
                 fixed = TRUE,
                 random = FALSE,
                 backtransf = F,
                 # cluster ? 
                 # subgroup ? 
)

## forest plot of usage

png(file = "forestplot_washing.png", width = 5000, height = 2000, res = 500)
forest.meta(m.gen_usage_washing,
           leftcols = c("Authors", "Intervention"),
           digits =6,
           col.random = "Red",
           xlab = "Effect Sizes",
           col.square = "Blue")       
```


```{r}
##dishwasher 
m.gen_usage_dishwasher <- metagen(TE = z_value,
                 seTE = z_variance,
                 data = data_usage_dishwasher,
                 studlab = Authors,
                 sm = "ZCOR",
                 fixed = FALSE,
                 random = TRUE,
                 backtransf = F,
                 )

## forest plot of usage
png(file = "forestplot_dishwasher.png", width = 5000, height = 2000, res = 500)
forest.meta(m.gen_usage_dishwasher,
           leftcols = c("Authors", "Intervention"),
           digits =6,
           col.random = "Red",
           xlab = "Effect Sizes",
           col.square = "Blue")

 
```


```{r}
##refrigerator
m.gen_usage_refrigerator <- metagen(TE = z_value,
                 seTE = z_variance,
                 data = data_usage_refrigerator,
                 studlab = Authors,
                 sm = "ZCOR",
                 fixed = FALSE,
                 random = TRUE,
                 backtransf = F,
                 )

## forest plot of usage

png(file = "forestplot_refrigerator_u.png", width = 5000, height = 2200, res = 500)
forest.meta(m.gen_usage_refrigerator,
           leftcols = c("Authors", "Intervention"),
           digits =6,
           col.random = "Red",
           xlab = "Effect Sizes",
           col.square = "Blue")

 
           
```

```{r}
##heatpump
m.gen_usage_heat_pump <- metagen(TE = z_value,
                 seTE = z_variance,
                 data = data_usage_heat_pump,
                 studlab = Authors,
                 sm = "ZCOR",
                 fixed = FALSE,
                 random = TRUE,
                 backtransf = F,
                 )

## forest plot of usage
png(file = "forestplot_heatpump_u.png", width = 5000, height = 1800, res = 500)
forest.meta(m.gen_usage_heat_pump,
           leftcols = c("Authors", "Intervention"),
           digits =6,
           col.random = "Red",
           xlab = "Effect Sizes",
           col.square = "Blue")

 
```


```{r}
##lighting
m.gen_usage_lighting <- metagen(TE = z_value,
                 seTE = z_variance,
                 data = data_usage_lighting,
                 studlab = Authors,
                 sm = "ZCOR",
                 fixed = FALSE,
                 random = TRUE,
                 backtransf = F,
                 )

## forest plot of usage

png(file = "forestplot_lighting_u.png", width = 5000, height = 1500, res = 500)

forest.meta(m.gen_usage_lighting,
           leftcols = c("Authors", "Intervention"),
           digits =6,
           col.random = "Red",
           xlab = "Effect Sizes",
           col.square = "Blue")

 

```


```{r}
##airconditioning
m.gen_usage_ac <- metagen(TE = z_value,
                 seTE = z_variance,
                 data = data_usage_ac,
                 studlab = authors,
                 sm = "ZCOR",
                 fixed = FALSE,
                 random = TRUE,
                 backtransf = F,
                 )

## forest plot of usage

png(file = "forestplot_air_u.png", width = 5500, height = 2600, res = 500)

forest.meta(m.gen_usage_ac,
           leftcols = c("authors", "Intervention"),
           digits =6,
           col.random = "Red",
           xlab = "Effect Sizes",
           col.square = "Blue")
```

```{r}
# done until here
########Pooled effect sizes (generic inverse variance pooling method)

###washing machine
pooled_washing <- metacor(cor = r_effect_size_obsversation,
        n = total_observations,
        data = data_usage_washing,
        fixed =  F,
        random = T,
        method.tau = "REML",
        hakn = T)
pooled_washing
##studies 9
## r = -0.0001

###referigerator
pooled_refrigerator <- metacor(cor = r_effect_size_obsversation,
        n = total_observations,
        data = data_usage_refrigerator,
        fixed =  F,
        random = T,
        method.tau = "REML",
        hakn = T)
pooled_refrigerator
##dishwasher
pooled_dishwasher <- metacor(cor = r_effect_size_obsversation,
        n = total_observations,
        data = data_usage_dishwasher,
        fixed =  F,
        random = T,
        method.tau = "REML",
        hakn = T)
pooled_dishwasher

##heatpump

pooled_heatpump <- metacor(cor = r_effect_size_obsversation,
        n = total_observations,
        data = data_usage_heat_pump,
        fixed =  F,
        random = T,
        method.tau = "REML",
        hakn = T)

pooled_heatpump

##air conditioning
pooled_airconditioning <- metacor(cor = r_effect_size_obsversation,
        n = total_observations,
        data = data_usage_air,
        fixed =  F,
        random = T,
        method.tau = "REML",
        hakn = T)

pooled_airconditioning

## lighting
pooled_lighting <- metacor(cor = r_effect_size_obsversation,
        n = total_observations,
        data = data_usage_lighting,
        fixed =  F,
        random = T,
        method.tau = "REML",
        hakn = T)

pooled_lighting
```

```{r}
##### Pooled values for appliance and intervention

###Washing Machine
## label and washing machine

metacor(cor = r_effect_size_obsversation,
        n = total_observations,
        data = data_usage_washing_label,
        fixed =  F,
        random = T,
        method.tau = "REML",
        hakn = T)
## reabte and washing machine
metacor(cor = r_effect_size_obsversation,
        n = total_observations,
        data = data_usage_washing_rebate,
        fixed =  F,
        random = T,
        method.tau = "REML",
        hakn = T)
```

```{r}
###Dishwasher
## info and dihswasher

metacor(cor = r_effect_size_obsversation,
        n = total_observations,
        data = data_usage_dishwasher_information,
        fixed =  F,
        random = T,
        method.tau = "REML",
        hakn = T)
## rebate and dishwasher
metacor(cor = r_effect_size_obsversation,
        n = total_observations,
        data = data_usage_dishwasher_rebate,
        fixed =  F,
        random = T,
        method.tau = "REML",
        hakn = T)
```


```{r}
###Refrigerator
## info and ref

metacor(cor = r_effect_size_obsversation,
        n = total_observations,
        data = data_usage_refrigerator_information,
        fixed =  F,
        random = T,
        method.tau = "REML",
        hakn = T)

## label and ref
metacor(cor = r_effect_size_obsversation,
        n = total_observations,
        data = data_usage_refrigerator_label,
        fixed =  F,
        random = T,
        method.tau = "REML",
        hakn = T)

## rebate and ref
metacor(cor = r_effect_size_obsversation,
        n = total_observations,
        data = data_usage_refrigerator_rebate,
        fixed =  F,
        random = T,
        method.tau = "REML",
        hakn = T)
```

```{r}
###heat pump

##heat pump & info
metacor(cor = r_effect_size_obsversation,
        n = total_observations,
        data = data_usage_heat_pump_information,
        fixed =  F,
        random = T,
        method.tau = "REML",
        hakn = T)

## feedback and heatpump
metacor(cor = r_effect_size_obsversation,
        n = total_observations,
        data = data_usage_heat_pump_feedback,
        fixed =  F,
        random = T,
        method.tau = "REML",
        hakn = T)

## rebate and heatpump
metacor(cor = r_effect_size_obsversation,
        n = total_observations,
        data = data_usage_heat_pump_rebate,
        fixed =  F,
        random = T,
        method.tau = "REML",
        hakn = T)
```

```{r}
###lighting

## info and light
metacor(cor = r_effect_size_obsversation,
        n = total_observations,
        data = data_usage_lighting_information,
        fixed =  F,
        random = T,
        method.tau = "REML",
        hakn = T)

## feedback and lighting
metacor(cor = r_effect_size_obsversation,
        n = total_observations,
        data = data_usage_lighting_feedback,
        fixed =  F,
        random = T,
        method.tau = "REML",
        hakn = T)
```

```{r}
### air con

## air & feedback
metacor(cor = r_effect_size_obsversation,
        n = total_observations,
        data = data_usage_air_feedback,
        fixed =  F,
        random = T,
        method.tau = "REML",
        hakn = T)

## info and air
metacor(cor = r_effect_size_obsversation,
        n = total_observations,
        data = data_usage_air_information,
        fixed =  F,
        random = T,
        method.tau = "REML",
        hakn = T)

## rebate and air
metacor(cor = r_effect_size_obsversation,
        n = total_observations,
        data = data_usage_air_rebate,
        fixed =  F,
        random = T,
        method.tau = "REML",
        hakn = T)
```
